title

### 2013-02-04 paper.tex
Changed table

Our overall conclusions are as follows:
\begin{enumerate}
\item The US will not see a drastic increase in water usage. We estimate in Section \ref{total} that the overall increase in water usage by 2025 will not exceed 2 \%. In fact many regions will see a net decrease in water usage, according to our models.
\item In the absence of overall water usage growth, our water management plan focuses on being robust to short-term crises like droughts. To solve the latter we propose a national grid of high-volume pipelines to improve connectivity and transport water to areas with increased seasonal water needs.
\item Second, using cluster analysis we identify areas in which the growth in water demand will be most severe and recommend specific infrastructure in these regions to balance increased demand.
\item Finally, we make recommendations on how to improve sustainability and decrease environmental impact, especially pollution and the depletion of groundwater.
\end{enumerate}

@@

We model the overall water requirements of the United States by applying
a linear regression to the total amount of water used across the country
as a whole.

\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
Year & 1985 & 1990 & 1995 & 2005 & 2013 (proj.) & 2025 (proj.)\tabularnewline
\hline 
Total Water Use (Mgal/day) & 398465 & 407980 & 401554 & 410465 & 413695 & 419355\tabularnewline
\hline 
\end{tabular}

@@

A secondary and extremely desirable effect of high national connectivity is decreased reliance on groundwater. As a case study to understand the overexploitation of aquifers, consider the High Plains aquifer, which supplies water to Colorado, Kansas, Nebraska, New Mexico, Oklahoma, South Dakota, Texas, and Wyoming, some of the most agricultural states in the US \ref{key-19}.
Due to overexploitation many areas have experienced severe water-level decline, an average of 12.8 feet. While 9 percent of areas suffered decline as severe as 50 feet, only a bare 2 percent saw any significant (over 10 feet) of water-level rise since predevelopment. It is estimated that 9 percent of the total storage in this massive and essential groundwater supply was exhausted by 2005.

>>>>

Our overall conclusions are as follows:
\begin{enumerate}
\item The US will not see a drastic increase in water usage. We estimate in Section \ref{total} that the overall increase in water usage by 2025 will not exceed 2 \%. In fact many regions will see a net decrease in water usage, according to our models.
\item In the absence of overall water usage growth, our water management plan focuses on being robust to short-term crises like droughts. To solve the latter we propose a national grid of high-volume pipelines to improve connectivity and transport water to areas with increased seasonal water needs.
\item Using cluster analysis we identify areas in which the growth in water demand will be most severe and recommend specific infrastructure in these regions to balance increased demand.
\item Finally, we make recommendations on how to improve sustainability and decrease environmental impact, especially pollution and the depletion of groundwater.
\end{enumerate}

@@

We model the overall water requirements of the United States by applying
a linear regression to the total amount of water used across the country
as a whole in Table 1.

\vspace{5mm}
\begin{table}[h]\label{waterusetable}
\begin{center}
\begin{tabular}{|c|c|}

\hline

Year & Total Water Use (Mgal/day)\tabularnewline

\hline

\hline

1985 & 398465\tabularnewline

\hline

1990 & 407980\tabularnewline

\hline

1995 & 401554\tabularnewline

\hline

2005 & 410465\tabularnewline

\hline

2013 (proj.) & 413695\tabularnewline

\hline

2025 (proj.) & 419355\tabularnewline

\hline

\end{tabular}
\caption{Total water use in 1985-2005 and projected values in 2013 and 2025.}
\end{center}
\end{table}
\vspace{5mm}

@@

A secondary and extremely desirable effect of high national connectivity is decreased reliance on groundwater. As a case study to understand the overexploitation of aquifers, consider the High Plains aquifer, which supplies water to Colorado, Kansas, Nebraska, New Mexico, Oklahoma, South Dakota, Texas, and Wyoming, some of the most agricultural states in the US \cite{key-19}.
Due to overexploitation many areas have experienced severe water-level decline, an average of 12.8 feet. While 9 percent of areas suffered decline as severe as 50 feet, only a bare 2 percent saw any significant (over 10 feet) of water-level rise since predevelopment. It is estimated that 9 percent of the total storage in this massive and essential groundwater supply was exhausted by 2005.
